\begin{thebibliography}{9}
    \bibitem{ddos_survey_1} Saman Taghavi Zargar, James Joshi and David Tipper {\em A Survey of Defense Mechanisms Against Distributed Denial of Service (DDoS) Flooding Attacks}, 2013. ()

    \bibitem{ddos_survey_2} s

    \bibitem{ddos_motivations} Tasnuva Mahjabin, Yang Xiao, Guang Sun and Wangdong Jiang {\em A survey of distributed denial-of-service attack, prevention, and mitigation techniques}, 2017. (https://journals.sagepub.com/doi/10.1177/1550147717741463)

    \bibitem{ddos_survey_3} Neha Agrawal and Shashikala Tapaswi {\em Defense schemes for variants of distributed denial-of-service (DDoS) attacks in cloud
    computing: A survey}, 2017. (https://doi.org/10.1080/19393555.2017.1282995)

    \bibitem{ddos_survey_4} Jasmeen Kaur Chahal, Abhinav Bhandari and Sunny Behal {\em Distributed Denial of Service Attacks: A Threat or Challenge}, 2019. (https://doi.org/10.1080/13614576.2019.1611468)

    \bibitem{ddos_kaspersky} kaspersky securitylist.com {\em DDoS Report - DDoS attacks in Q4 2020
    }, 2020. (https://securelist.com/ddos-attacks-in-q4-2020/100650/)
  
    \bibitem{ddos_kaspersky_q3_2020} kaspersky securitylist.com {\em DDoS Report - DDoS attacks in Q3 2020
    }, 2020. (https://securelist.com/ddos-attacks-in-q4-2020/100650/)    

    \bibitem{slide_mirai} slide mirai

    \bibitem{reti_neurali_libro} Michael A. Nielsen  {\em Neural Networks and Deep Learning }, Determination Press, 2015. (http://neuralnetworksanddeeplearning.com/)   

    \bibitem{anomaly_detection_classification} \url{https://www.researchgate.net/publication/332078049_Data_Analytics_Methods_for_Anomaly_Detection_Evolution_and_Recommendations}

    \bibitem{anomaly_detection_techniques} \url{https://www-sciencedirect-com.ezproxy.biblio.polito.it/science/article/pii/S1084804515002891#f0015}

    \bibitem{esempio_keras}  Keras documentation 
    
    \bibitem{anomaly_detection_survey_1_network}  Mohiuddin Ahmed, Abdun Naser and Mahmood JiankunHu, {\em A survey of network anomaly detection techniques }, 2016. (https://doi.org/10.1016/j.jnca.2015.11.016)

    \bibitem{anomaly_detection_survey_2_deep_learning} Raghavendra Chalapathy and  Sanjay Chawla, {\em Deep Learning for Anomaly Detection: A Survey }, 2019. (https://arxiv.org/abs/1901.03407v2)
    
    \bibitem{anomaly_detection_survey_3} Varun Chandola, Arindam Banerjee and Vipin Kumar, {\em Anomaly detection: A survey}, 2009. (https://dl.acm.org/doi/abs/10.1145/1541880.1541882)
    
    \bibitem{cilium_ebpf} https://docs.cilium.io/en/stable/bpf/
    \bibitem{cilium_xdp} https://docs.cilium.io/en/stable/concepts/ebpf/intro/

    \bibitem{risso_ebpf} slide risso
     
    \bibitem{ebpf.io} https://ebpf.io/what-is-ebpf

    \bibitem{imperva_amplification} https://www.imperva.com/blog/ntp-flood-explained/

    \bibitem{imperva_ddos_trends} \url{https://www.imperva.com/docs/DS_Incapsula_The_Top_10_DDoS_Attack_Trends_ebook.pdf}
    
    \bibitem{imperva_ddos_report} \url{https://www.imperva.com/resources/resource-library/reports/global-ddos-threat-landscape/}

    \bibitem{keras_esempio} \url{https://keras.io/examples/timeseries/timeseries_anomaly_detection/}


    % \bibitem{esempio_keras} Keras {\em Keras documentation }, 2020. (https://keras.io/examples/timeseries/timeseries_anomaly_detection)

    %% da qui va cancellata
    % \bibitem{gal} G.~Galilei, {\em Nuovi studii sugli astri medicei}, Manuzio, Venetia, 1612.

    % \bibitem{tor1} E.~Torricelli, in ``La pressione barometrica'', {\em Strumenti

    %         Moderni}, Il Porcellino, Firenze, 1606.
    % \bibitem{tor2} E.~Torricelli e A.~Vasari, in ``Delle misure'', {\em Atti Nuovo
    %         Cimento}, vol.~III, n.~2 (feb. 1607), p.~27--31.

    % \bibitem{duane1964} Duane J.T., \emph{Learning Curve Approach To Reliability Monitoring}, IEEE Transactions on Aerospace, Vol. 2, pp. 563-566, 1994

    % % altri riferimenti da usare come esempi.

    % \bibitem{chiesa2008} Chiesa S., \emph{Affidabilità, sicurezza e manutenzione
    %     nel progetto dei sistemi}, CLUT, gennaio 2008
    % \bibitem{chiesa2}Chiesa S., Fioriti M., Fusaro R., \emph{On Board System
    %     Technological  Level Improvement Effect on UAV MALE}
    % \bibitem{bigliano2010} Bigliano M., \emph{Sicurezza nell'installazione di un velivolo
    %     senza pilota MALE; applicazione di metodologia di Zonal Safety
    %     Analysis al velivolo del Progetto SAvE}, Politecnico di Torino,
    % maggio 2010
    % \bibitem{astrid2012} Chiesa S., Di Meo G.A., Fioriti M., Medici G., Viola N.,
    % \emph{ASTRID - Aircraft on board Systems sizing and TRade-off
    %     analysis in Initial Design}, Research Bulletin, Warsaw University
    % of Technology, Institute of Aeronautics and Applied Mechanics,
    % p. 1-28, 17-19, ottobre 2012

\end{thebibliography}
